\documentclass{article}
\usepackage[normalem]{ulem}
\usepackage{fixltx2e}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage[top=2cm,bottom=2cm,left=3cm,right=3cm]{geometry}
\usepackage{multicol}
\usepackage{float}


\begin{document}
\pagebreak
    \section{Project Management}
\subsection{Term 1}
During the first term our main objective was to research and investigate the problems with the existing emergency services. We had weekly meetings during which the tasks for the upcoming week were discussed and split between us. Everybody from the team had to research a specific topic and report back to the rest of the members.
During the meetings possible issues with the existing systems were identified.\\

During the second part of the term we started brainstorming possible solutions to the identified problems. Each solution was broken down to very high level details. Further discussions were then conducted in order to evaluate the scope and the impact of the suggested solutions. When doing this we also involved the opinion of several people working in the emergency services as well as ordinary people that would benefit from the improved systems. Solutions that were too trivial or impossible with the currently existing technologies were discarded. \\ 

By the end of the term we managed to choose the best ideas and decided to proceed with designing them.\\

\subsection{Term 2}

Having identified the problems that we wanted to tackle we were able to start designing the solutions.
Given that the requirements were not clear at the beginning of the process we decided that an Agile approach will be more suitable for designing the system. The group members were assigned to different modules of the project. High level user stories were created for all of the components. The designing process was divided into iterations where each iteration was covering several user stories. By the end of each iteration a working prototype was designed. Weekly meetings were organized where each team member was reporting the progress from the past week. Ideas and suggestions were also exchanged. \\
\subsection{Used Services}

Trello was used as a tool for organizing and keeping track of the work. Google Drive was used as a main storage and as a tool for collaboration between team members. Facebook group was also created and was used as a main communication channel.

\end{document}