\documentclass[]{article}
\usepackage{../myPackage}


\begin{document}
\section{Bibliography}
\begin{enumerate}[label={[\arabic*]}]

\item S. Rogers,\\
'Mortality statistics: every cause of death in England and Wales, visualised | Datablog',\\
the Guardian, 2011. [Online].\\
Available: http://www.theguardian.com/news/datablog/2011/oct/28/mortality-statistics-causes-death-england-wales-2010. \\{}
[Accessed: 16- Feb- 2015]

\item NHS England,\\ 'Consensus Paper on Out-of-Hospital Cardiac Arrest in England',\\ NHS England, 2014 [Online].\\ Available: https://www.resus.org.uk/pages/OHCA\_consensus\_paper.pdf.\\{} [Accessed: 16- Feb- 2015]

\item D. Campbell,\\ 'Chances of surviving cardiac arrest in England 'dire'',\\ The Guardian, 2012 [Online]. \\Available: http://www.theguardian.com/society/2012/nov/19/chances-surviving-cardiac-arrest-dire.\\{} [Accessed: 16- Feb- 2015]

\item T. Lindner, E. Søreide, O. Nilsen and M. Wenche Torunn,\\ 'Good outcome in every fourth resuscitation attempt is achievable—An Utstein template report from the Stavanger region', 2011 [Online]. \\Available: http://www.sahlgrenska.se/upload/SU/omrade\_molndal/ambulans/Good\%20outcome\%20in
\%20every\%20fourth\%20resuscitation\%20attempt\%20is\%20achievable.\%20Stavanger.pdf. \\{}[Accessed: 16- Feb- 2015]

\item NHS England, \\'Increase bystander initiated CPR by increasing proportion of population trained in CPR from 3.8m people to 5 million nationally', 2014 [Online].\\ Available: http://www.england.nhs.uk/wp-content/uploads/2014/02/pm-fs-3-2.pdf. \\{}[Accessed: 16- Feb- 2015]

\item Smslivraddare.se, \\'Info om hjärtstopp | SMSLivräddare', 2015. [Online].\\ Available: http://www.smslivraddare.se/info-om-hjartstopp. \\{} [Accessed: 16- Feb- 2015]

\item Hscic.gov.uk, \\'Find data - Health \& Social Care Information Centre', 2015. [Online].\\ Available: http://www.hscic.gov.uk/catalogue/PUB11062. \\{} [Accessed: 16- Feb- 2015]

\item P. Stephenson, \\'Text messages are saving Swedes from cardiac arrest', \\Quartz, 2015. [Online]. \\Available: http://qz.com/138334/text-messages-are-saving-swedes-from-cardiac-arrest/. \\{}[Accessed: 16- Feb- 2015]

\item A. Sifferlin,\\ 'How Sweden’s New Text Message Plan Is Saving Cardiac Arrest Victims | TIME.com', \\TIME.com, 2015. [Online].\\ Available: http://healthland.time.com/2013/10/23/how-swedens-new-text-message-plan-is-saving-cardiac-arrest-victims/. \\{}[Accessed: 16- Feb- 2015]

\item Developer.android.com, \\'Google Cloud Messaging | Android Developers', 2015. [Online].\\ Available: https://developer.android.com/google/gcm/index.html. \\{}[Accessed: 19- Feb- 2015]

\item G. drain, \\'Google Cloud Messaging and less battery drain',\\ Stackoverflow.com, 2015. [Online].\\ Available: http://stackoverflow.com/a/12124927. \\{}[Accessed: 19- Feb- 2015]

\item Wenda.baba.io, \\'Is GCM service reliable for large scale push notification?', 2015. [Online]. \\Available: http://wenda.baba.io/questions/1527378/is-gcm-service-reliable-for-large-scale-push-notification.html. \\{}[Accessed: 19- Feb- 2015]

\item Google Developers, \\{}'Orchestrating iOS Push Notifications on Google Cloud Platform', 2015. [Online].\\{} Available: https://cloud.google.com/developers/articles/ios-push-notifications/. \\{}[Accessed: 19- Feb- 2015]

\item  Developer.android.com, \\{}'Implementing GCM Client on Android | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/google/gcm/client.html. \\{}[Accessed: 21- Feb- 2015]

\item  Developer.android.com,\\{} 'Server Reference | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/google/gcm/server-ref.html.\\{} [Accessed: 04- Mar- 2015]

\item  Developer.android.com,\\{} 'LatLng | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/reference/com/google/android/gms/maps/model/LatLng.html. \\{}[Accessed: 04- Mar- 2015]

\item  Developer.android.com, \\{}'Common Intents | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/guide/components/intents-common.html.\\{} [Accessed: 04- Mar- 2015]

\item  Google Developers, \\{}'Markers', 2015. [Online].\\{} Available: https://developers.google.com/maps/documentation/android/marker. \\{}[Accessed: 04- Mar- 2015]
1
\item  Developer.android.com, \\{}'Geocoder | Android Developers', 2015. [Online].\\{} Available: http://developer.android.com/reference/android/location/Geocoder.html. \\{}[Accessed: 07- Mar- 2015]

\item  Developer.android.com, \\{}'Address | Android Developers', 2015. [Online].\\{} Available: http://developer.android.com/reference/android/location/Address.html. \\{}[Accessed: 07- Mar- 2015]

\item  Developer.android.com, \\{}'Distance to Location | Android Developers', 2015. [Online].\\{} Available: http://developer.android.com/reference/android/location/Location.html. \\{}[Accessed: 07- Mar- 2015]

\item  Developer.android.com,\\{} 'Notifications | Android Developers', 2015. [Online].\\{} Available: http://developer.android.com/design/patterns/notifications.html.\\{} [Accessed: 07- Mar- 2015]

\item  Developer.android.com,\\{} 'Implementing Collapseable Messages | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/google/gcm/server.html.\\{}[Accessed: 08- Mar- 2015]

\item  BBC News,\\{} 'Ambulance service miss emergency response times', 2013 [Online].\\{} Available: http://Ambulance service miss emergency response times. \\{}[Accessed: 08- Mar- 2015]

\item  Developer.android.com, \\{}'GCM Cloud Connection Server (XMPP) | Android Developers', 2015. [Online].\\{} Available: http://developer.android.com/google/gcm/ccs.html. \\{}[Accessed: 13- Mar- 2015]

\item  Stackoverflow.com,\\{} 'Why and how is push-notification (like GCM) battery efficient?', 2015. [Online].\\{} Available: http://stackoverflow.com/questions/22663778/why-and-how-is-push-notification-like-gcm-battery-efficient. \\{}[Accessed: 13- Mar- 2015]

\item  Java.dzone.com, \\{}'Upstream Messages with Google Cloud Messaging | Javalobby', 2015. [Online]. \\{}Available: http://java.dzone.com/articles/upstream-messages-google-cloud?page=0,1. \\{}[Accessed: 13- Mar- 2015]

\item  Developer.android.com, \\{}'Getting the Last Known Location | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/training/location/retrieve-current.html. \\{}[Accessed: 13- Mar- 2015]

\item  Rightleftrightwrong.com, \\{}'Right, Left, Right, Wrong! - Handedness Statistics', 2015. [Online].\\{} Available: http://www.rightleftrightwrong.com/statistics.html.\\{} [Accessed: 18- Mar- 2015]

\item  BBC News, \\{}'Ambulance times slowest since 2011', 2014. [Online].\\{} Available: http://www.bbc.co.uk/news/uk-wales-30631210. \\{}[Accessed: 18- Mar- 2015]

\item  Londonambulance.nhs.uk, \\{}'London Ambulance Service - What happens when you call 999', 2015. [Online].\\{} Available: http://www.londonambulance.nhs.uk/calling\_999/what\_happens\_when\_you\_call\_999.aspx. \\{}[Accessed: 18- Apr- 2015]

\item  Londonambulance.nhs.uk,\\{} 'London Ambulance Service - How we use your personal information', 2015. [Online].\\{} Available: http://www.londonambulance.nhs.uk/talking\_with\_us/use\_your\_personal\_information.aspx. \\{}[Accessed: 27- Apr- 2015]

\item  TopTenREVIEWS,\\{} 'Video Calling Phones Review - TopTenREVIEWS', 2015. [Online]. \\{}Available: http://video-calling-phones-review.toptenreviews.com/.\\{} [Accessed: 27- Apr- 2015]

\item  Wikipedia, \\{}'Smartphones', 2015. [Online].\\{} Available: http://en.wikipedia.org/wiki/Smartphone.\\{} [Accessed: 27- Apr- 2015]

\item  Gsmarena.com, \\{}'GSMArena.com - GSM phone reviews, news, opinions, votes, manuals and more...', 2015. [Online].\\{} Available: http://www.gsmarena.com/. \\{}[Accessed: 27- Apr- 2015]

\item  Mobilemastinfo.com, \\{}'Stats and Facts', 2015. [Online].\\{} Available: http://www.mobilemastinfo.com/stats-and-facts/. \\{}[Accessed: 27- Apr- 2015]

\item  Wikipedia, \\{}'5G', 2015. [Online].\\{} Available: http://en.wikipedia.org/wiki/5G.\\{} [Accessed: 27- Apr- 2015]

\item  Support.skype.com, \\{}'How much bandwidth does Skype need?', 2015. [Online]. \\{}Available: https://support.skype.com/en/faq/FA1417/how-much-bandwidth-does-skype-need. \\{}[Accessed: 27- Apr- 2015]

\item  Support.google.com, \\{}'Live encoder settings, bit rates and resolutions - YouTube Help', 2015. [Online].\\{} Available: https://support.google.com/youtube/answer/2853702?hl=en-GB.\\{} [Accessed: 27- Apr- 2015]

\item  Wikipedia,\\{} 'Real-time Transport Protocol', 2015. [Online]. \\{}Available: http://en.wikipedia.org/wiki/Real-time\_Transport\_Protocol. \\{}[Accessed: 27- Apr- 2015]

\item G. Kelly,\\{} 'H.265 vs VP9: 4K video codecs explained', Trustedreviews.com, 2014. [Online].\\{} Available: http://www.trustedreviews.com/opinions/h-265-vs-vp9-4k-video-codes-explained. \\{}[Accessed: 27- Apr- 2015]

\item  Wikipedia,\\{} 'VP9', 2015. [Online].\\{} Available: http://en.wikipedia.org/wiki/VP9. \\{}[Accessed: 27- Apr- 2015]

\item S. Shankland, \\{}'Google urges fast adoption of VP9 video compression - CNET', CNET, 2013. [Online]. \\{}Available: http://www.cnet.com/news/google-urges-fast-adoption-of-vp9-video-compression/.\\{} [Accessed: 27- Apr- 2015]

\item R. Wingard, \\{}'The Video Codec Fight: H.265 vs. VP9', Blog.euclidiq.com, 2014. [Online].\\{} Available: http://blog.euclidiq.com/video-compression-blog/the-video-codec-fight-h.265-vs.-vp9. \\{}[Accessed: 27- Apr- 2015]

\item S. Formats,\\{} 'Supported Media Formats | Android Developers', Developer.android.com, 2015. [Online].\\{} Available: http://developer.android.com/guide/appendix/media-formats.html.\\{} [Accessed: 27- Apr- 2015]

\item  Ustream Support,\\{} 'Internet connection and recommended encoding settings', 2015. [Online].\\{} Available: https://ustream.zendesk.com/entries/22962268-Internet-connection-and-recommended-encoding-settings.\\{} [Accessed: 27- Apr- 2015]

\item  Wikipedia,\\{} 'WebM', 2015. [Online].\\{} Available: http://en.wikipedia.org/wiki/WebM.\\{} [Accessed: 27- Apr- 2015]

\item  Webmproject.org, \\{}'The WebM Project', 2015. [Online]. \\{}Available: http://www.webmproject.org/.\\{} [Accessed: 27- Apr- 2015]

\item  Emergencysms.org.uk, \\{}'SMS to the emergency services | EmergencySMS', 2015. [Online].\\{} Available: http://www.emergencysms.org.uk/. \\{}[Accessed: 27- Apr- 2015]

\item  Wikipedia, \\{}'Short Message Service', 2015. [Online]. \\{}Available: http://en.wikipedia.org/wiki/Short\_Message\_Service. \\{}[Accessed: 27- Apr- 2015]

\item  Emergencysms.org.uk, \\{}'How to send text | EmergencySMS', 2015. [Online].\\{} Available: http://www.emergencysms.org.uk/how\_to\_send\_text.php. \\{}[Accessed: 27- Apr- 2015]

\item  Emergencysms.org.uk, \\{}'News | EmergencySMS', 2012. [Online].\\{} Available: http://www.emergencysms.org.uk/news.php. \\{}[Accessed: 27- Apr- 2015]

\item  Safenetwork.org.uk, \\{}'Deaf awareness | Identifying deafness | The Safe Network', 2011. [Online].\\{} Available: http://www.safenetwork.org.uk/training\_and\_awareness/pages/deaf-awareness.aspx. \\{}[Accessed: 27- Apr- 2015]

\item  Wikipedia,\\{} 'WebSocket', 2015. [Online].\\{} Available: http://en.wikipedia.org/wiki/WebSocket.\\{} [Accessed: 27- Apr- 2015]

\item  Findlaw.co.uk, \\{}'Hoax 999 calls - Crime and Justice', 2015. [Online].\\{} Available: http://www.findlaw.co.uk/law/criminal/crimes\_a\_z/500552.html.\\{} [Accessed: 27- Apr- 2015]

\item  Developer.android.com,\\{} 'Notification | Android Developers', 2015. [Online].\\{} Available: https://developer.android.com/reference/android/app/Notification.html.\\{} [Accessed: 28- Apr- 2015]

\item  W3.org, \\{}'Hypertext Transfer Protocol Specification', 2015. [Online].\\{} Available: http://www.w3.org/Protocols/rfc2616/rfc2616.txt. \\{}[Accessed: 29- Apr- 2015]

\item P. Barber,\\{} 'Phill Barber's Blog: Client Side vs Server Side Session',\\{} Phillbarber.blogspot.co.uk, 2014. [Online].\\{} Available: http://phillbarber.blogspot.co.uk/2014/02/client-side-vs-server-side-session.html. \\{}[Accessed: 29- Apr- 2015]

\item The JSON Data Interchange Format, \\{}1st ed. ECMA International, 2013 [Online]. \\{}Available: http://www.ecma-international.org/publications/files/ECMA-ST/ECMA-404.pdf.\\{} [Accessed: 29- Apr- 2015]

\item  GitHub, \\{}'swagger-api/swagger-spec', 2015. [Online]. \\{}Available: https://github.com/swagger-api/swagger-spec.\\{} [Accessed: 29- Apr- 2015]

\item N. Carey,\\{} 'Establishing Pedestrian Walking Speeds', 2005 [Online].\\{} Available: http://www.westernite.org/datacollectionfund/2005/psu\_ped\_summary.pdf. \\{}[Accessed: 24- Apr- 2015]

\item  Json-schema.org, \\{}'JSON Schema - Documentation', 2015. [Online].\\{} Available: http://json-schema.org/documentation.html. \\{}[Accessed: 29- Apr- 2015]

\end{enumerate}

\end{document}